PCA

### 2019-10-18 analysis/11_pcalda.Rmd
new fig

# confirm
row.names(countData) == row.names(colData)
```

@@

a <- ggplot(mypcadf, aes(x = PC1, y = PC2, color = colData$treatment)) +
  geom_point() + labs(x = "PC1: 35.9%", y = "PC2: 32.5%") + theme_minimal(base_size = 8)  +
  theme(legend.title = element_blank(), legend.position = "left")
a

b <-  fviz_pca_var(mypca,  labelsize = 3 , axes.linetype = "blank", 
                   repel = TRUE ,
                  select.var= list(contrib = 10))
b

@@

# MDS

```{r MDS}
euclidist <- dist(countData) # euclidean distances between the rows
fit <- cmdscale(euclidist,eig=TRUE, k=2) # k is the number of dim
x <- fit$points[,1]
y <- fit$points[,2]

plot(x, y, xlab="Coordinate 1", ylab="Coordinate 2",
  main="Metric MDS", type="n")
text(x, y, labels = row.names(countData), cex=.7)
```

@@

c  <- ggplot(tsne_df_cols, aes(x = V1, y = V2, shape = sex, color = tissue)) +
  geom_point(size = 2) +
  theme_minimal(base_size = 6) +
  scale_color_manual(values = c("#d95f02","#1b9e77", "#7570b3")) +
  theme(legend.position = "top")

d <- ggplot(tsne_df_cols, aes(x = V1, y = V2, shape = sex, color = treatment)) +
  geom_point(size = 2) +
  theme_minimal(base_size = 6) +
  theme(legend.position = "top")

plot_grid(c,d)
```

>>>>

# confirm
row.names(countData) == row.names(colData)

euclidist <- dist(countData) # euclidean distances between the rows
```

@@

a <- ggplot(mypcadf, aes(x = PC1, y = PC2, 
                         color = colData$treatment, 
                         shape = colData$tissue)) +
  geom_point() + labs(x = "PC1: 35.9%", y = "PC2: 32.5%") + theme_minimal(base_size = 6)  +
  theme(legend.title = element_blank(), legend.position = "left")
a

b <-  fviz_pca_var(mypca,  labelsize = 3 , axes.linetype = "blank", 
                   repel = TRUE ,
                  select.var= list(contrib = 6))
b

@@

@@

c  <- ggplot(tsne_df_cols, aes(x = V1, y = V2, shape = sex, color = tissue)) +
  geom_point(size = 2) +
  theme_minimal(base_size = 6) +
  scale_color_manual(values = c("#d95f02","#1b9e77", "#7570b3")) +
  theme(legend.position = "top") +
  labs(x = "tSNE 1", y = "tSNE 2")

d <- ggplot(tsne_df_cols, aes(x = V1, y = V2, shape = sex, color = treatment)) +
  geom_point(size = 2) +
  theme_minimal(base_size = 6) +
  theme(legend.position = "top") +
  labs(x = "tSNE 1", y = "tSNE 2")

cd <- plot_grid(c,d)
cd
```

# combined pca tsne

```{r pca.tSNE, fig.width=6, fig.height=6}
plot_grid(ab,cd, ncol = 1)

plot_grid(a + theme(legend.position = "none"),
          b + theme(axis.text = element_blank()) + ggtitle(NULL), 
          c + theme(legend.position = "none"),
          d + theme(legend.position = "none"))
```
